---
title: 'Peer-graded Assignment: Getting and Cleaning Data Course Project Week4'
author: "Moon Choi"
date: '2017 3 12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Set Library and download Data.

This step check packages and download raw data.
If packages are not inst
```{r warning = FALSE, message= FALSE }
requiredPackages <- c("plyr", "dplyr", "sqldf")
installReuiredPackages <- requiredPackages[!(requiredPackages %in% utils::installed.packages()[,"Package"])]
if(length(installReuiredPackages)) install.packages(installReuiredPackages, repos = "http://cran.us.r-project.org")
library("plyr")
library("dplyr")
library("sqldf")

```


OS <-.Platform$OS.type
dataSetNm <- "initDataSet.zip"
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
if(OS == "unix"){
  download.file(fileUrl, dataSetNm, method = "curl")
}else{
  download.file(fileUrl, dataSetNm)
}
unzip(dataSetNm)

## 2. Data Cleaning
**Realted assignment requirements**

>1.Merges the training and the test sets to create one data set.
>2.Extracts only the measurements on the mean and standard deviation for each measurement.
>3.Uses descriptive activity names to name the activities in the data set.
>4.Appropriately labels the data set with descriptive variable names. 

First step is find mean and standard deviation feature from *Features.txt*. Row sequence number of this will be use to filter mean and standard deviation from train and test set.

```{r warning = FALSE}
ACTIVITY_LABELS <- read.table("UCI HAR Dataset/activity_labels.txt",col.names = c("ACTV_CD","ACTV_NM"), stringsAsFactors = FALSE)
FEATURE_LIST <- read.table("UCI HAR Dataset/features.txt", col.names = c("FTR_SEQ","FTR_NM"), stringsAsFactors = FALSE)
FEATURE_TARGET = sqldf("SELECT * FROM FEATURE_LIST WHERE FTR_NM LIKE '%mean()%' or FTR_NM LIKE '%std()%' ")

FEATURE_TARGET <- FEATURE_TARGET %>% 
mutate( 
        FTR_TP_NM = gsub("-mean()", "", .$FTR_NM)
      , FTR_TP_NM = gsub("-std()", "", FTR_TP_NM)
      , MEAN_CD = regexpr(".*mean().*", .$FTR_NM)
      , STD_CD  = regexpr(".*std().*" , .$FTR_NM)
      ) %>% 
mutate( STAT_TP_CD =
        case_when(.$MEAN_CD == 1 ~ "Mean", .$STD_CD  == 1 ~ "Std" )
      ) %>%
select(1,2,3,6)

head(FEATURE_TARGET)
```

##### Data Frame variable description

1. FEATURE_TARGET

Column Name | Description 
----------|---------------------------------------------------------
FTR_SEQ | Featuer sequance number. This number matched with train and test column number.
FTR_NM | Featuer name
FTR_TP_NM | Featuer type name. Remove *'-mean()'* and *'-std()'* string from FTR_NM.
STAT_TP_CD | Featuer stattic type code. Value is Mean or STD


Filter *X_train.txt*, *X_test.txt* column based on FTR_SEQ column of FEATURE_TARGET.
And combine all train column (X_$*$.txt, Y_$*$.txt, subject_$*$.txt. $*$ means train or test.)
After combine column add *ORIGIN_SET* to trace where data come from. "TST" is test data set and "TRN" is training data set.
Test an d train data row combined one data set and save as DATA_SET_INIT data frame.
```{r}
TRAIN_SET_X <- read.table("UCI HAR Dataset/train/X_train.txt")[, FEATURE_TARGET$FTR_SEQ]
names(TRAIN_SET_X) <- FEATURE_TARGET$FTR_NM
TRAIN_SET_Y <- read.table("UCI HAR Dataset/train/Y_train.txt")
TRAIN_SET_Y[,1] = ACTIVITY_LABELS[TRAIN_SET_Y[,1],2]
names(TRAIN_SET_Y) <- 'ACTV_NM'
TRAIN_SUBJECT <- read.table("UCI HAR Dataset/train/subject_train.txt")
names(TRAIN_SUBJECT) <- 'SUBJ_NM'
TRAIN_DATA_SET <- cbind(ORIGIN_SET =c("TRN"),TRAIN_SET_Y, TRAIN_SUBJECT, TRAIN_SET_X)

TEST_SET_X <- read.table("UCI HAR Dataset/test/X_test.txt")[, FEATURE_TARGET$FTR_SEQ]
names(TEST_SET_X) <- FEATURE_TARGET$FTR_NM
TEST_SET_Y <- read.table("UCI HAR Dataset/test/Y_test.txt")
TEST_SET_Y[,1] = ACTIVITY_LABELS[TEST_SET_Y[,1],2]
names(TEST_SET_Y) <- 'ACTV_NM'
TEST_SUBJECT <- read.table("UCI HAR Dataset/test/subject_test.txt")
names(TEST_SUBJECT) <- 'SUBJ_NM'
TEST_DATA_SET <- cbind(ORIGIN_SET =c("TST"),TEST_SET_Y, TEST_SUBJECT, TEST_SET_X)

DATA_SET_INIT <- rbind(TRAIN_DATA_SET, TEST_DATA_SET)
```

## 3. Create new data set and save data set 

**Realted assignment requirements**

>5.From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

Now I create new data set with the average of each variable for each activity and each subject.
And save raw data set and new data set to the root folder.
New data frame name of new data set is DATA_SET.
```{r}
DATA_SET <- ddply(DATA_SET_INIT, .(SUBJ_NM, ACTV_NM), function(x) colMeans(x[, 4:69]))

write.table(DATA_SET_INIT, "UCI HAR Dataset/Mean_And_Std_Raw_Data.txt", row.name=FALSE)
write.table(DATA_SET, "UCI HAR Dataset/Mean_And_Std_Average_Data.txt", row.name=FALSE)
```
